# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

First we load our data to the dataframe
```{r}
data<-read.csv("activity.csv", header = TRUE, stringsAsFactors=FALSE)
head(data)
```



## What is mean total number of steps taken per day
Plot a number of steps for each day
```{r warning=FALSE}
databydate<-aggregate(steps~date, data, sum)
plot(strptime(databydate$date, format = "%Y-%m-%d"), databydate$steps, type='h', xlab="", ylab="Steps")
```
And a histogram for it
```{r}
hist(databydate$steps,col = "blue", xlab="Steps")
```
And calculate mean and median for steps per day

```{r}
daymean<-mean(databydate$steps)
daymedian<-median(databydate$steps)
```
So mean is `r daymean` and median is `r daymedian`


## What is the average daily activity pattern?
Plot daily activity pattern
```{r}
databyinterval<-aggregate(steps~interval, data, mean)
plot(databyinterval$interval, databyinterval$steps, type='l', xlab="interval", ylab="Steps")
```
We can see that max steps contains interval 835

## Imputing missing values
1. Report total NA in dataset
```{r}
sum(is.na(data))
```

2. Replace NA's with mean steps for given interval

```{r}
newdata<-data
newdata[is.na(newdata),1]<-databyinterval$steps[match(newdata$interval[is.na(newdata)], databyinterval$interval)]
```
 After that remade our plots from first exercise
```{r warning=FALSE}
databydate<-aggregate(steps~date, newdata, sum)
plot(strptime(databydate$date, format = "%Y-%m-%d"), databydate$steps, type='h', xlab="", ylab="Steps")
```
And a histogram for it
```{r}
hist(databydate$steps,col = "red", xlab="Steps")
```
And calculate mean and median for steps per day

```{r}
daymean<-mean(databydate$steps)
daymedian<-median(databydate$steps)
```
So mean is `r daymean` and median is `r daymedian`
As we can see mean and mediannow the same, and mean hasn't change
 

## Are there differences in activity patterns between weekdays and weekends?
Create factor first (I'm use ukrainian locale, so day of weeks may appear strange)
```{r}
newdata$day<-factor(ifelse(as.POSIXlt(strptime(newdata$date, format = "%Y-%m-%d"))$wday == 0 | as.POSIXlt(strptime(newdata$date, format = "%Y-%m-%d"))$wday==6,"weekend","weekday"))
```


Next plot 
```{r}
databyinterval<-aggregate(steps~interval*day, newdata, mean)
library(lattice)
xyplot(steps ~ interval   | day, databyinterval, type="l")
```
